Rates and delay times of type Ia supernovae in the Dark Energy Survey

### 2021-03-15 draft.tex

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/mass_hist_linlog_sn_field_BC03.png}
    \caption{Upper: Distribution of the stellar mass of the SN host (green dot-dashed) and field galaxies (orange and grey solid) used in the analysis. Lower: As upper for field galaxies, but shown on a log scale.  The distribution closely matches data from the ZFOURGE survey at $0.5<z<0.75$ (magenta dots). The difference between the raw counts and the $V_{\mathrm{max}}$ corrected counts (Section \ref{sec:incompleteness}) is minimal. 
    \label{fig:mass_hist_hosts_field}}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/CSFH_MD14.png}
    \caption{Cosmic star-formation history (CSFH) as approximated by our model (cyan curve) and as a best fit to observations \citep{Madau2014}.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
    \label{fig:csfh}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/mass_hist_linlog_sn_field_BC03.png}
    \caption{Upper: Distribution of the stellar mass of the SN host galaxies. The raw (green dashed) and spectroscopic-efficiency-weighted (blue dot-dashed; Section \ref{subsec:incompletenss_SN_hosts}) histograms are both normalised. Lower: As upper but for field galaxies, and shown on a log scale.  The distribution closely matches data from the ZFOURGE survey at $0.5<z<0.75$ (magenta dots). The difference between the raw counts (grey dotted) and the $V_{\mathrm{max}}$ corrected counts (orange solid; see Section \ref{sec:incompleteness}) is minimal. 
    \label{fig:mass_hist_hosts_field}}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/CSFH_MD14.png}
    \caption{Cosmic star-formation history (CSFH) as approximated by our model (cyan solid) and as a best fit to observations (magenta dashed; \citealt{Madau2014}).}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
    \label{fig:csfh}
\end{figure}
